### 2022-12-06 README.Rmd
Reimplemented rescale proxy feature in linrampfitter.R
Also restructured files related to reproducing results. Other minor changes. Cleaned up old plots and unused files

---
output: github_document
---

@@

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 8,
  fig.height = 4,
  dev = "png",
  out.width = "90%"
)
```

>>>>

---
output: github_document:
  html_preview: false
---

@@

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 8,
  fig.height = 4,
  dev = "png",
  out.width = "100%"
)
```

### 2022-12-06 inst/reproduce_results/results.Rmd
Reimplemented rescale proxy feature in linrampfitter.R
Also restructured files related to reproducing results. Other minor changes. Cleaned up old plots and unused files

<!-- Paper_results_2.md is generated from paper_results_2.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/results2-",
  dev = "png",
  out.width = "80%"
)
```

@@

```{r simex}
rm(list=ls())
require(stats)
library(ggplot2)
set.seed(123)
n=1000
y0 = 1000
z0 = 1200
phi=0.8; sigma=1.2
depth = z0+seq(from=0.5,500,length.out=1000)
depth2 = depth^2/depth[1]^2 #normalize for stability

>>>>

<!-- results.md is generated from results.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/reproduce/results/results-",
  dev = "png",
  out.width = "100%"
)
```

@@

```{r simex}
rm(list=ls())
require(stats)
library(ggplot2)
set.seed(123)
n=1000
y0 = 1000
z0 = 1200
phi=0.8; sigma=1.2
depth = z0+seq(from=0.5,500,length.out=1000)
depth2 = depth^2/z0 #normalize for stability
